Galaxy Zoo: Classifications for Galaxies in HST Legacy Imaging

### 2014-03-04 writeup/gz_hubble_data.tex
Updated my grant acknowledgement
and testing what happens!
Small edits

AEGIS has1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers ~710 arcmin$^2$.

GOODS targeted 2 fields, GOODS-N and GOODS-S, imaging in 4 filters -- F435W (B), F606W (V), F775W (i), and F850LP (z). The mean exposure times vary, from 1000 - 2100 seconds. The images have been dithered to a pixel scale of 0.03 ''/pixel and covers at total area of ~320 arcmin$^2$ (160 arcmin$^2$ per field). The filters that Griffith et al uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.

COSMOS has 1 orbit (2028 seconds) in the F814W (I band) filter and has been dithered to 0.05 ''/pixel; it covers the largest area, ~1.8 deg$^2$.

GEMS has 1 orbit (2160 and 2286 seconds) in the F606W and F850LP filters, with a pixel scale of 0.03 ''/pixel; it covers ~800 arcmin$^2$

@@

So we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi).

@@

The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications) and surface brightnesses, and also picked ideal something for different target redshifts in HST imaging.

 Here are the selection criteria for the categories

@@

This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \texttt{http://www.galaxyzoo.org/volunteers}. Galaxy Zoo 2 was developed with the help of a grant from The Leverhulme Trust.

>>>>

\begin{itemize}
\item AEGIS has1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers ~710 arcmin$^2$.

\item GOODS targeted 2 fields, GOODS-N and GOODS-S, imaging in 4 filters -- F435W (B), F606W (V), F775W (i), and F850LP (z). The mean exposure times vary, from 1000 - 2100 seconds. The images have been dithered to a pixel scale of 0.03 ''/pixel and covers at total area of ~320 arcmin$^2$ (160 arcmin$^2$ per field). The filters that Griffith et al uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.

\item COSMOS has 1 orbit (2028 seconds) in the F814W (I band) filter and has been dithered to 0.05 ''/pixel; it covers the largest area, ~1.8 deg$^2$.

\item GEMS has 1 orbit (2160 and 2286 seconds) in the F606W and F850LP filters, with a pixel scale of 0.03 ''/pixel; it covers ~800 arcmin$^2$
\end{itemize}

@@

So we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi) to produce images from these typical of those observed in the HST surveys.

@@

The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications), with a range of surface brightnesses, and also picked ideal something for different target redshifts in HST imaging.

 The selection criteria for the different morphological categories

@@

This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \texttt{http://www.galaxyzoo.org/volunteers}. Galaxy Zoo 2 was developed with the help of a grant from The Leverhulme Trust. KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
